---
title: "shiny_poj_notes"
author: "Mark Schott"
date: "April 20, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploratory Data Analysis on the Consumer Complaint Database regarding US Financial Products and Services


## Using rgdal to handle SpatialPolygonDataFrames

So after reading <http://zevross.com/blog/2015/10/14/manipulating-and-mapping-us-census-data-in-r-using-the-acs-tigris-and-leaflet-packages-3/>, shown to me by Chao. It seems that handling SpatialPolygonDataFrames (SPDF) is easier than I was doing earlier which manually converted the object to a data frame, merged, then recast back to a SPDF. 
```{r SPDF, eval = F}
library(rgdal)
states = readOGR('states.json')
states@data = merge(states@data, other_df, by = 'common header')
```

## Dealing with the large CSV

I'm also having trouble considering how to initially load the data into my shiny app. Currently I'm manually loading the csv into a data frame but the csv is quite large (around 300M). This clearly is not an acceptable solution for production. I could save it as an .rda or .rds and load it which may be much faster. Ideally, I would be making specific queries into a relational database using SQLite or MYSQL but the syntax for shiny is annoying to provide the flexibility which I desire. 

These are the list of the data files I need
1. Consumer complaints database
2. Abbreviations dataframe
3. Population information
4. json spatial object of us states and territories

## Other plots to use

I think that plotting the word count for a specific company versus the number of complaints could be an interesting plot

## Things to do

1. Subset inputs per tab    (Done)
2. Add legend to map        (Done)
3. Change labels of bar plots    (Done)
4. Incorporate mosaic plots
5. Handle the wells fargo freeze up for the word map
6. Remove obvious financial related words
7. Get date slider to work properly for map        (Done)
8. Get leaflet proxy to work
9. Plot just latitude and longitude points
10. Sentiment analysis on word cloud
11. Add title of company to word cloud, Add text displaying total word count by the word cloud
12. Change label so that it shows up clearly on the map.    (Done)
13. Assemble slides into cohesive story, thinking something to do with states and company
14. Display counts in map by company make one input for that     (Done)
15. Change company selector from drop down to search input     (Done)
16. Analyze difference from Date.received to Date.sent.to.company    (Nope)
17. Mosaic plot pick two variables to sample and display (too large too display all?)
18. Change max n to adjust for dates                    (Done, removed from bar plot)
19. Add second variable to bar plots                    (Done)
20. Remove companies who have no text                   (Done)
21. Show word bubble by state and do random sampling of text
22. Plot word counts versus complaint counts. (More complaints more words... so?)
23. Hide/Change legend position for bar plot        (Done)
24. Change bar plot y label to Total Count          (Done)
25. Add plot to map tab that shows count by date by State            (Done)
26. Analyze time series data
    a. Day of the week, group by month analysis       (Done)
      - Frequency by day of the week/month            (Done)
    b. group data into weeks/months to smooth out deviations
27. Try to understand why the map gets mixed up when the counts are really low    (Done)  

## Story
1. Counts by state normalized
2. Time frequency with corresponding statistical tests
  a. Day of the week and month
3. Complaints predicting events such as the wells fargo event (show a vertical line on the TS plot)
4. Disproportionate submitted.via by state (shown well with mosaic plot)
5. 